\bf Forecasts Reconciliation: A geometric view with new insights on bias correction.

### 2019-08-17 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
background in intro

	A collection of multiple time series with some aggregation structure arises in many disciplines such as manufacturing, engineering, marketing, medicine, etc. These are often known as hierarchical time series. Making coherent forecasts for these series that are in line with the inherent aggregation constraints is an essential requirement for decision making. Early studies on this literature use a single level forecasting approaches. That is, forecasting the series in a single level of the hierarchy and then aggregate or disaggregate these forecasts to get coherent forecasts for remaining series. The well known Bottom-up \citep{Dunn1976} and Top-down \citep{Gross1990, Athanasopoulos2009} methods are examples for these traditional methods. Multiple studies also discuss the relative advantages and disadvantages of these methods, for example, \citet{Schwarzkopf1988, Kahn1998, Lapide1998, Fliedner2001}.

	A shortcoming of these traditional methods is that they do not use all the information available in the hierarchy to make coherent forecasts. To overcome this issue, \cite{Hyndman2011} propose to utilise all the information available in the hierarchy via a ``Reconciliation" process. This is a two-stages process where the first stage involves making forecasts for all series in the hierarchy without considering the aggregation constraints (also known as base forecasts), which is then followed by the reconciliation stage that combines these forecasts imposing the aggregation constraints of the hierarchy. A later study by \cite{WicEtAl2019} proposed to optimally combine the base forecasts by minimising the trace of the mean squared errors of reconciled forecasts where they derived an analytical solution to produce reconciled forecasts. An important feature of this method is that it imposes the correlation structure of the whole hierarchy to produce reconciled point forecasts.

>>>>

	Multivariate time series that follow an aggregation structure arise in many disciplines such as manufacturing, engineering, marketing and medicine\todo{include references}. Forecasts of these series should adhere to aggregation constraints to ensure aligned decision making. Earlier studies achieved this by only forecasting a single level of the hierarchy and then either aggregating in a bottom up fashion \citep{Dunn1976} or disaggregating in a Top-down \citep{Gross1990, Athanasopoulos2009} fashion.  For reviews of these approaches see \citet{Schwarzkopf1988, Kahn1998, Lapide1998, Fliedner2001}.

	In contrast to these approaches \cite{Hyndman2011} proposed forecasting all series in the hierarchy, referring to these as {\em base} forecasts.  Since base forecasts were produced independently they were not guaranteed to adhere to aggregation constraints and could be improved via further adjustment.  A framework was proposed whereby the forecasts were assumed to follow a regression model.  The predicted values from this model were guaranteed to adhere to the linear constraints by construction and could thus be used as a new set of forecasts.  This approach and later modifications have subsequently been shown to outperform bottom up and top down approaches in a variety of empirical settings\todo{references}.

	Some theoretical insight into the good performance of forecast reconciliation methods has been provided by \cite{VanErven2015a} and \cite{WicEtAl2019}.  Both papers provide a proof that reconciliation is guaranteed to improve base forecasts.  The latter paper also proposes a particular version of reconciliation known as the Minimum Trace (MinT) method.  This is optimal in the sense of minimising the trace of reconciled forecast error covariance matrix under the assumption that base forecasts are unbiased.
